---
title: "Homework-2 - Code/Plots for Problem 5"
author: "Aji John"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Solution for 5(a)

### Our theoretical expression is of the form x_t+h = beta* h + alpha*x_t , with h=70,

```{r,echo=FALSE,include=FALSE}
alpha=1
beta=2
n=100

xt <- function(n)  
{
  set<-c()
  for(i in 1:n)
  {  
    intv <- alpha + (beta * i)
    set<-c(set,intv)
  }    
  return(set)
}    

xt_100 <- xt(100)

fit <- lm(xt_100[1:30]~xt_100[71:100])
```

```{r,echo=FALSE,include=TRUE}
plot(xt_100[1:30],xt_100[71:100],type="b",lwd=2,
ylim=c(0,250),xlim=c(0,100),col="black",
xlab="x_t",ylab="x_t+70",
main="Lag 70 plot")

```

## Verification  by plotting residuals

### Furthermore, Our linear expression from the plot is x_t+70 = 1 * x_t + 140, slope = 1, and intercept is 140. Slope = alpha = 1, Intercept = beta * h. thus matching the theoretical expression.


```{r,echo=FALSE,include=TRUE}
plot(fit)
```

#Solution for 5(b)

```{r,echo=FALSE,include=FALSE}
row_hat <- function(h)
{
  
  top_hat<- 0
  x_bar <- mean(xt_100)
  for (t in 1:100-h)
  {
    
     x_tplush <- xt_100[t+h]
     x_t <- xt_100[t]
     top_hat <- top_hat + (( x_tplush - x_bar) * ( x_t - x_bar))
  }
  
  bot_hat<- 0
  
   for (t in 1:100)
  {
    
     x_t <- xt_100[t]
     bot_hat <- bot_hat + ( ( x_t - x_bar)^2)
  }
  
  print(paste('th ' ,top_hat))
  print(paste('bh' , bot_hat))
  return(top_hat/bot_hat)
}

for(h in 0:99)
{
  print(row_hat(h))
}
```


## Plotting using the acf

```{r,echo=FALSE,include=TRUE}
 acf(xt_100, lag.max=99, plot=TRUE)
``` 


#Solution for 5(c)

The approximations do matchup with the plot in part c