---
title: "Homework 5"
output:
  pdf_document: default
  html_document: default
Author: Aji John
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 14 b



```{r,include=TRUE}
sim.a <- function(n=100,a=-2,b=1,c=pi/4)
{
  Zt <- rnorm(n+2)
  a + b*Zt[3:(n+2)] + c*Zt[1:n]
}

sim.b <- function(n=100,a=-3,b=1,c=pi/4)
{
  Zt <- rnorm(n+2,sd = sqrt(0.25))
  a + b*Zt[3:(n+2)] + c*Zt[1:n]
}

set.seed(42)

```

## Problem 14 b

```{r,include=TRUE}


df <- data.frame()

for (k in 1:1000){
  
  row_i <-  as.vector(acf(sim.a(), lag.max=4, plot=FALSE)$acf[2:5])
  df <- rbind(df,row_i)
}

acf.tss.mat.1000 <- as.matrix(df)
colnames(acf.tss.mat.1000) <- c('rho_1','rho_2','rho_3', 'rho_4')

df_corr <- data.frame()

for (i in 1:4){
 b <- c()

 for (j in 1:4)
 {
   b <- c(b, cor(acf.tss.mat.1000[,i],acf.tss.mat.1000[,j]))  
 }
 df_corr <- rbind(df_corr,b)
}

df_cov <- data.frame()

for (i in 1:4){
 b <- c()

 for (j in 1:4)
 {
   b <- c(b, cov(acf.tss.mat.1000[,i],acf.tss.mat.1000[,j]))  
 }
 df_cov <- rbind(df_cov,b)
}
 colnames(df_corr) <-  c('cor_1','cor_2','cor_3', 'cor_4')
 colnames(df_cov) <-  c('cov_1','cov_2','cov_3', 'cov_4')

```

## Sample mean
```{r}

colMeans(acf.tss.mat.1000)

```
## Correlation Matrix
```{r}

knitr::kable(df_corr)

```

## Covariance Matrix
```{r}

knitr::kable(df_cov)

```

### It is very much in sync with what large sample theory suggests, have done some spot checking below

#### Lets calculate W(4,4)  ( Same as W(3,3) ) using the Bartlett matrix
    ((2*(pi^2))/(16 * (1+pi/4)^2) + 1 )/100 =  0.01387026
#### Also, lets  calculate W(1,1) using the Bartlett matrix    
    ((2*pi^2)/(16 * (1+pi/4)^2) + 1 + (2*pi/(4*(1+(pi/4)^2))) )/100 = 0.02358542
#### Also, lets  calculate W(3,1) using the Bartlett matrix    
    (((pi^2))/(16 * (1+pi/4)^2) + ( (2*pi/(4*(1+(pi/4)^2))))) /100 = 0.01165029  
#### Once in negative, can be taken as tending towards 0, so W(1,2),W(1,4), W(2,3) & W(3,4) are all zeros.


# Changing the value , a = -2, sd =4

```{r,include=TRUE}

#create matrix from vectors
set.seed(42)
df2 <- data.frame()

for (k in 1:1000){
  
  row_i <-  as.vector(acf(sim.b(), lag.max=4, plot=FALSE)$acf[2:5])
  df2<- rbind(df2,row_i)
}

acf.tss.mat.1000.v2 <- as.matrix(df2)
colnames(acf.tss.mat.1000.v2) <- c('rho_1_2','rho_2_2','rho_3_2', 'rho_4_2')

df_corr_2 <- data.frame()

for (i in 1:4){
 b <- c()

 for (j in 1:4)
 {
   b <- c(b, cor(acf.tss.mat.1000.v2[,i],acf.tss.mat.1000.v2[,j]))  
 }
 df_corr_2 <- rbind(df_corr_2,b)
}

df_cov_2 <- data.frame()

for (i in 1:4){
 b <- c()

 for (j in 1:4)
 {
   b <- c(b, cov(acf.tss.mat.1000.v2[,i],acf.tss.mat.1000.v2[,j]))  
 }
 df_cov_2 <- rbind(df_cov_2,b)
}
 colnames(df_corr_2) <-  c('cor_1_2','cor_2_2','cor_3_2', 'cor_4_2')
 colnames(df_cov_2) <-  c('cov_1_2','cov_2_2','cov_3_2', 'cov_4_2')

```
## Sample mean 2
```{r}

colMeans(acf.tss.mat.1000.v2)

```

## Covariance Matrix 2
```{r}

knitr::kable(df_cov_2)

```
## Correlation Matrix 2
```{r}

knitr::kable(df_corr_2)

```


### Changing the variance (sqrt(0.25)) and 'a'(-3) does not seem to change the Mean,Correlation or Covariance matrix. I would say ecause of large sample, it would still be normally distributed.


