---
title: "Mt Rainier Timeseries Analysis"
output: beamer_presentation
author: "Aji John, Buckley Lab, UW Biology"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


Climate
========================================================

```{r, echo=FALSE,include=FALSE}
library(tidyverse)

theme_Publication <- function(base_size=14, base_family="helvetica") {
      (theme_foundation(base_size=base_size, base_family=base_family)
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.margin = unit(0, "cm"),
               legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))
      
}

```

</br>

### The term originally denoted a zone of the earth between two lines of latitude, then any region of the earth, and later, a region considered with reference to its atmospheric conditions. (Apple dictionary)

One climate variable - Temperature
========================================================

### Important as it directly relates to productivity in plants/animals. 

```{r, echo=FALSE,warning=FALSE,include=FALSE,message=FALSE}
climatedata <- read.csv("data/AB08-A2_hourly.csv")
climatedata$dt <- strptime(climatedata$DATE, format = "%Y-%m-%d %H:%M:%S")
climatedata$dt_txn <- as.POSIXct(climatedata$DATE,ormat = "%Y-%m-%d %H:%M:%S")
# Add month column
# Add day column
# Add hour column
climatedata$month <-format(climatedata$dt_txn,"%m")
climatedata$day <- format(climatedata$dt_txn,"%d")
climatedata$hour <- format(climatedata$dt_txn,"%H")
climatedata$year <- substring(as.character(climatedata$DATE),1,4)
```

How is it diced ? Temperature
========================================================

<br>

### How is it used ?

<br>

Parameter     | Context
------------- | -------------
Minimum       | Day/Month/Season/Year
Maximum       | Day/Month/Season/Year
Diurnal       | Daily (Max - min)

<br>
<br>

#### A study might use combination of these parameters, but could get complicated by adding other environmental attributes. 

Case study - Mt Rainier sites
========================================================


```{r, echo=FALSE,warning=FALSE,fig=TRUE,message=FALSE,fig.align = "center", fig.width=3, fig.height=4}
#ggplot needs date in POSIXct

onest <- read.csv("data/AM16-A2_hourly.csv")
onest$dt <- strptime(onest$DATE, format = "%Y-%m-%d %H:%M:%S")
str(onest)
### define function to do filtering ...

filter.with.padding <- function(x,the.filter,iter=1)
{
    q <- (length(the.filter)-1)/2
    n <- length(x)
    w <- stats::filter(c(rep(x[1],q),x,rep(x[n],q)),the.filter)[(q+1):(q+n)]
    if(iter > 1) for(i in 2:iter) w <- filter(c(rep(w[1],q),w,rep(w[n],q)),the.filter)[(q+1):(q+n)]
    return(w)
}

plot.ACFest <- function(ts, main=NULL, n.lags=40)
{
    ts.acf <- acf(ts, lag.max=n.lags, plot=FALSE)
    n.ts <- length(ts)
    xs <- 1:n.lags
    ys <- ts.acf$acf[2:(n.lags+1)]
    plot(xs,ys,typ="h",xlab="h  (lag)",ylab="ACF",ylim=c(-1,1),col="blue",main=main)
    points(xs,ys,col="red",cex=0.5)
    xs <- 1:n.lags
    xs[1] <- xs[1] - 0.25
    xs[n.lags] <- xs[n.lags] + 0.25
    lines(xs,1.96*sqrt(n.ts-xs)/n.ts,col="magenta",lty="dashed")
    lines(xs,-1.96*sqrt(n.ts-xs)/n.ts,col="magenta",lty="dashed")
    abline(h=0,lty="dashed")
    CI.hw <- 1.96/sqrt(n.ts)
    lines(c(0.75,n.lags+0.25),rep(CI.hw,2),col="blue",lty="dashed")
    lines(c(0.75,n.lags+0.25),rep(-CI.hw,2),col="blue",lty="dashed")
    return(ts.acf$acf)
}
### overhead III-2

plot(onest$dt,onest$series_xts,col="blue",xlab="year",typ="l",
     ylab=expression(x[t]),main=expression(paste("Site AB08: A2",
       " Series from MT Rainier , WA")))
```

<br>


========================================================
#### Monthly mean

```{r, echo=FALSE,warning=FALSE,fig=TRUE,error=FALSE,message=FALSE,fig.align = "center",out.width = '60%'}

```

Classical Decomposition Model 
========================================================

<br>



{\displaystyle y_{t}=T_{t}+S_{t}+Z_{t},}






Seasonal  
========================================================
#### DJF - Winter - Across all years by month

```{r, echo=FALSE,warning=FALSE,fig=TRUE,message=FALSE,error=FALSE,fig.align = "center",out.width = '60%'}
#ggplot needs date in POSIXct
onest$dt_txn <- as.POSIXct(onest$DATE,ormat = "%Y-%m-%d %H:%M:%S")
# Add month column
# Add day column
# Add hour column
onest$month <-format(onest$dt_txn,"%m")
onest$day <- format(onest$dt_txn,"%d")
onest$hour <- format(onest$dt_txn,"%H")


#subset it to only 9 years
# Removed 1288 rows containing missing values 
oneset_9yrs <- onest %>% select(c('dt_txn','series_xts','year','month','day','hour')) %>% 
  filter(!is.na(series_xts) & year > 2008 & year < 2017) %>% as.data.frame() 



#Summarize by months
oneset_9yrs_by_month <- oneset_9yrs %>% group_by(year,month) %>% summarise(min_t=min(series_xts),max_t= min(series_xts),mean_t=mean(series_xts),rows=n()) %>% as.data.frame()

# Add key
oneset_9yrs_by_month$xaxis <- as.double(paste(oneset_9yrs_by_month$year,oneset_9yrs_by_month$month,sep = '.'))

#1 .042 
#2 .125 
#3 .208 
#4 .292 
#5 .375 
#6 .458 
#7 .542 
#8 .625 
#9 .708 
#10 .792  
#11 .875 
#12 .958 

#create new xaxis
oneset_9yrs_by_month$xaxisred <- "0"
#Redo x-axis
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="01",]$xaxisred = "042"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="02",]$xaxisred = "125"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="03",]$xaxisred = "208"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="04",]$xaxisred = "292"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="05",]$xaxisred = "375"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="06",]$xaxisred = "458"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="07",]$xaxisred = "542"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="08",]$xaxisred = "625"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="09",]$xaxisred = "708"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="10",]$xaxisred = "792"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="11",]$xaxisred = "875"
oneset_9yrs_by_month[oneset_9yrs_by_month$month=="12",]$xaxisred = "958"

oneset_9yrs_by_month$nxaxis <- as.double(paste(oneset_9yrs_by_month$year,oneset_9yrs_by_month$xaxisred,sep = '.'))

# For every year we should have 12 values

#oneset_9yrs_by_month %>% ggplot(aes(year,mean_t,color=month)) + geom_point() +xlab("Time") + ylab("Mean Temperature (deg C)")

#Applying moving average filter
m.hat.oneset <- filter.with.padding(oneset_9yrs_by_month$mean_t,c(1/24,rep(1/12,11),1/24))

#plot(oneset_9yrs_by_month$xaxis,oneset_9yrs_by_month$mean_t,col="blue",xlab="year",typ="b",
#     ylab=expression(paste(x[t]," and ", hat(m)[t]," (deg C)")),main="Monthly Temp Values",cex=0.5)
#lines(oneset_9yrs_by_month$xaxis,m.hat.oneset,col="red",lwd=2)

plot(oneset_9yrs_by_month$nxaxis,oneset_9yrs_by_month$mean_t,col="blue",xlab="year",typ="b",
     ylab=expression(paste(x[t]," and ", hat(m)[t]," (deg C)")),main="Monthly Temp Values",cex=0.5)
lines(oneset_9yrs_by_month$nxaxis,m.hat.oneset,col="red",lwd=2)

```


Temporal variation 
========================================================

<br>

### Important ? Growing Degree Days ~ Phenology




<br>
<br>

#### Other relationships - variation of it spatially

Diurnal 
========================================================
#### DJF - Winter - By year

```{r, echo=FALSE,warning=FALSE,fig=TRUE,error=FALSE,message=FALSE,fig.align = "center",out.width = '60%'}
#ggplot needs date in POSIXct

climatedata %>%  select(c("DATE","TZ","series_xts", "dt_txn","month","day","hour","year")) %>%filter(month %in% c('12','01','02')) %>% 
ggplot(aes(hour,series_xts,group=year,color=year)) + 
stat_smooth(se = FALSE) +  theme_minimal() +
ggtitle("Site AB08 - DJF Hourly Temperatures")+
xlab("Time of day") + ylab("Air Temperature")

```

Diurnal 
========================================================
#### JJA - Summer - By year

```{r, echo=FALSE,warning=FALSE,error=FALSE,fig=TRUE,message=FALSE,fig.align = "center",out.width = '60%'}
#ggplot needs date in POSIXct

climatedata %>%  select(c("DATE","TZ","series_xts", "dt_txn","month","day","hour","year")) %>%filter(month %in% c('06','07','08')) %>% 
ggplot(aes(hour,series_xts,group=year,color=year)) + 
stat_smooth(se = FALSE) +  theme_minimal() +
ggtitle("Site AB08 - JJA Hourly Temperatures")+
xlab("Time of day") + ylab("Air Temperature") 

```

How is it used ? Temperature
========================================================

<br>

### How is it used ?




<br>
<br>

#### Recorded in various ways, by daily, monthly or yearly